---
title: 'Programming Assignment 2: Lexical Scoping'
author: "Julian Posada"
date: "2023-02-04"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Science Specialization
### Course 2: Programming in R
#### Programming Assignment 2: Lexical Scoping

Write the following functions:

makeCacheMatrix: This function creates a special "matrix" object that can cache its inverse.

cacheSolve: This function computes the inverse of the special "matrix" returned by makeCacheMatrix above. If the inverse has already been calculated (and the matrix has not changed), then the cachesolve should retrieve the inverse from the cache.

Computing the inverse of a square matrix can be done with the solve function in R. For example, if X is a square invertible matrix, then solve(X) returns its inverse.

```{r}
source("cachematrix.R")
```

makeCacheMatrix: This function creates a special "matrix" object that can cache its inverse.

```{r}
makeCacheMatrix <- function(x = matrix()) # a matrix gets into variable x
{
        InverseCache <- NULL 
        set <- function(y) {    # the set function passes a matrix into x
                x <<- y 
                InverseCache <<- NULL # not inverse matrix yet
        } 
        get <- function() x # gets the source matrix
        set_inverse <- function(solve) InverseCache<<- solve # this function
        # receive the inverse of a matrix from another function and stores it 
        #as InverseCache
        get_inverse <- function() InverseCache # returns the cached inverse matrix
        list(set = set, get = get,
             set_inverse = set_inverse,
             get_inverse = get_inverse)# creates the Cache 
}
```

cacheSolve: This function computes the inverse of the special "matrix" returned by makeCacheMatrix above. If the inverse has already been calculated (and the matrix has not changed), then the cachesolve should retrieve the inverse from the cache.

```{r}
cacheSolve <- function(x) # it receives a matrix created with makeCacheMatrix()
{
        ## Return a matrix that is the inverse of 'x'
        m <- x$get_inverse()# if the inverse in cached, returns the cached inverse
        if(!is.null(m)) 
        {
                message("getting cached data")
                return(m)
        }
        message("creating new cache with the matrix:")
        data <- x$get()# if not, it creates the inverse matrix and stores it 
        print(data)# in the cache
        m <- solve(data)
        x$set_inverse(m)
        m #Returns the inverse
}
```

### Testing the results
#### function createMatrix creates a matrix.
code source: https://www.geeksforgeeks.org/inverse-of-matrix-in-r/

```{r}
createMatrix<- function()
{
        # R program to find inverse of a Matrix, 
        #source https://www.geeksforgeeks.org/inverse-of-matrix-in-r/
        
        # Create 3 different vectors
        # using combine method.
        a1 <- c(3, 2, 5)
        a2 <- c(2, 3, 2)
        a3 <- c(5, 2, 4)
        
        # bind the three vectors into a matrix 
        # using rbind() which is basically
        # row-wise binding.
        A <- rbind(a1, a2, a3)
}

```

### creating a testcase

```{r}
mat<- createMatrix()
test<- makeCacheMatrix(mat)
```
### using cacheSolve() for the first time.  NO cache expected

```{r}
cacheSolve(test)
```
### using cacheSolve() with the same data. Expecting data from cache

```{r}
cacheSolve(test)
```

